---
title: "esm_206_lab7_sr"
author: "Sarah Rohlfing"
date: "11/8/2021"
output: html_document
---

```{r setup, include=TRUE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)

```

intro to ggpairs

to create a pairs plot

```{r}
ggpairs(penguins)
```

```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))

ggplot(data= penguins, aes(x = bill_depth_mm, y = body_mass_g, group = species))+
  geom_point(aes(color = species))+
  geom_smooth(method = "lm")
```
multiple linear regression, penguins
use multiple linear regression to try to understand the relationship between multiple predictor variables and a single continuous outcome variable(body mass)

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)
penguin_lm
```
for every 1 mm increase in flipper length we can expect on average increase of  51.54g in body mass, considering all other variables remain constant

use the summary function to get more info

```{r}
summary(penguin_lm)
```

adjusted R-squared: 75 percent of the varience in our penguin body mass is explained in this model. 24 percent in varience that is not explained by our model. not good or bad. just a number telling us how much is explained

p-value od 2.2e-16, yes this model is doing a better job including these variables

use broom functions tidy and glance

broom: get coefficient summary in a data frame
broom::glance: get model summary in a data frame

```{r}
penguin_lm_tidy<- tidy(penguin_lm)
penguin_lm_tidy
```

using in-line code to refer to bill depth coefficient

`r penguin_lm_tidy$estimate[3]` put curser on it, hit cnrt, enter

```{r}
penguin_lm_glance <- glance(penguin_lm)
penguin_lm_glance
```
## try another model
thought hard, did a lit review, consulted with experts, deeply explored data, decided three most critical variables to include are:
flipper length
species
sex

```{r}
penguin_sex_species_lm <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)
penguin_sex_species_lm_tidy<- tidy(penguin_sex_species_lm)
penguin_sex_species_lm_tidy
penguin_sex_species_lm

```


ref: adelle, female

mass(g) = -365.82 + 20.82(flipper_length_mm)- 87.63(chinstrap)+836.3(gentoo)+530.38(male)


use broom augment
```{r}
augment(penguin_sex_species_lm)
```

## use plot to look at model diagnostics

```{r}
plot(penguin_sex_species_lm)
```

conceptual understanding and expertise allows me to responsibly determine that penguin species, sex, and flipper length are reasonable predictor variable (make sure you think about variables and diff variable combinations)
diagnostic plots all check out for normality of residuals, homoscedacity, and no worriesome outliers(<<last one is not an assumption)

##make output tables

```{r}
modelsummary(penguin_sex_species_lm)
```

using stargazer....stick to  model summary

```{r, results = "asis"}
stargazer(penguin_sex_species_lm, type = "html")
```


